This page will have visualizations that cover the following questions:

In which countries do alumnae report the highest frequency of
disagreements with family on key life decisions (education,
marriage, work, mobility, finances, body autonomy)?

How often are these disagreements resolved favorably, and does
resolution differ between 1-year and 5-year cohorts?

Are certain disagreement topics (like education or finances) more
likely to be resolved favorably across different contexts?

How does Agency relate to subsequent choices in education, work,
or marriage?

Example of what a viz could look like:

```{r}
library(tidyverse)
library(janitor)

# Brand palette
brand <- list(
  teal   = "#007AA4",
  green  = "#0C6F5A",
  yellow = "#FFC142",
  pink   = "#994263"
)

# Theme
theme_rtr <- function() {
  theme_minimal(base_family = "Georgia") +
    theme(
      plot.title = element_text(face = "bold", size = 18, color = "#111"),
      plot.subtitle = element_text(size = 12, color = "#333"),
      axis.title = element_text(size = 11, color = "#333"),
      axis.text  = element_text(size = 10, color = "#333"),
      panel.grid.minor = element_blank(),
      panel.grid.major.x = element_blank(),
      plot.margin = margin(6, 6, 6, 6)
    )
}
```

```{r}
# Data
df <- readr::read_csv("AlumnaeSurvey2324.csv")
print(df)
```
